EinsteinPy: Python for General Relativity

### 2020-01-24 paper.tex
Add bibliography

The relativistic theory of gravity paved its way to the ground in 1915?, when Prof. Albert Einstein published his paper on the general theory of relativity. This elegant and rigorous framework was a generalized version of gravity-free theory - special relativity, which he published earlier in 1905. Almost a hundred years after Einstein wrote down the equations of General Relativity, solutions of the Einstein field equations remain extremely difficult to find beyond those which exhibit significant symmetries.\\

@@

\begin{itemize}
\item \texttt The code must strictly adhere to the PEP8 Standards, on the top of it, the code must be linted with black to save the reviewer’s time identifying the changes made and reduce the diff generated because of the patch.
\item \texttt The imports in the code must be sorted using tools such as isort. 
\item \texttt The documentation follows numpy like docstrings, and a proper reStructured Text syntax is followed for writing the documentation.
\item \texttt The changelog is populated at release-time by the lead developer and the releasing developer
\end{itemize}
EinsteinPy further follows a trunk-based development model, which ensures a new branch for every minor release and new patch release made using the minor release branch. All the latest changes are kept on the master branch on GitHub and the relevant issues are closed as soon as the pull request solving it merges onto the master. A release having the changes is made at a later date. 
EinsteinPy only supports the latest bleeding-edge Python, Numpy and Astropy versions.  All the stable Python versions after Python 3.5 are supported. All the code snippets written follow the guidelines of numba in order to accelerate the Python code and make the simulations faster.

\section{The EinsteinPy Core Package} \label{sec:core}
This section explains in detail, the modules available within EinsteinPy core pacakge, their API and the purpose they serve.
\subsection{METRIC} \label{subsec:metric}
This module captures all the geometric and causal structure of specific spacetimes, and being able to calculate trajectories in a given space-time. 
The module derives its name from Metric Tensor, a tensorial quantity used to describe differential lengths, especially in a curved space-time. 
However, this module serves more than its usual definition and ultimately leads us to obtain geodesics of particles in a spacetime with high curvature, where notions of newtonian physics fail.
\subsubsection{Schwarzschild Metric} \label{subsubsec:sch}
Karl Schwarzchild pioneered the analysis of the relation between the size of black hole and its mass and this work paved the way for the first exact solution of Einstein's Field Equation under the limited case of single spherical non-rotating, non-charged body. 
The metric equation corrosponding to a space-time centred around a body in the above described conditions is given by,

@@

%The same equation can be written in a tensorial form as follows,

@@

We thank all the people that have made EinsteinPy what it is today.  
The organisations ESA, Poliastro and Indian institute of Technology, Mandi provided us with significant support and have our deepest thanks.
We would specially like to thank Dr.Abhay Ashtekar and  Dr. Timothy A. Gonsalves for their constant motivation.
Lastly, thanks to all our contributors who contrubuted towards building EinsteinPy.

@@

\software{astropy \citep{2013A&A...558A..33A},  
          Cloudy \citep{2013RMxAA..49..137F}, 
          SExtractor \citep{1996A&AS..117..393B}
          }

@@

\bibliography{sample63}{}
\bibliographystyle{aasjournal}

>>>>

The relativistic theory of gravity paved its way to the ground in 1916, when Prof. Albert Einstein published his paper on the general theory of relativity \citep{Einstein:1916vd}. This elegant and rigorous framework was a generalized version of gravity-free theory - special relativity, which he published earlier in 1905. Even after almost a hundred years after Einstein wrote down the equations of General Relativity, solutions of the Einstein field equations remain extremely difficult to find beyond those which exhibit significant symmetries.\\

@@

\begin{itemize}
\item \texttt The code must strictly adhere to the PEP8 Standards, on the top of it, the code must be linted with black to save the reviewer’s time identifying the changes made and reduce the diff generated because of the patch.
\item \texttt The imports in the code must be sorted using tools such as isort. 
\item \texttt The documentation follows numpy like docstrings, and a proper reStructured Text syntax is followed for writing the documentation.
\item \texttt The changelog is populated at release-time by the lead developer and the releasing developer
\end{itemize}
EinsteinPy further follows a trunk-based development model, which ensures a new branch for every minor release and new patch release made using the minor release branch. All the latest changes are kept on the master branch on GitHub and the relevant issues are closed as soon as the pull request solving it merges onto the master. A release having the changes is made at a later date. 
EinsteinPy only supports the latest bleeding-edge Python, Numpy\citep{numpy} and Astropy\citep{astropy:2018} versions.  All the stable Python versions after Python 3.5 are supported. All the code snippets written follow the guidelines of numba\citep{Lam2015NumbaAL} in order to accelerate the Python code and make the simulations faster.

\section{The EinsteinPy Core Package} \label{sec:core}
This section explains in detail, the modules available within EinsteinPy core package, their API and the purpose they serve.
\subsection{METRIC} \label{subsec:metric}
This module captures all the geometric and causal structure of specific space-times, and being able to calculate trajectories in a given space-time. 
The module derives its name from Metric Tensor, a tensorial quantity used to describe differential lengths, especially in a curved space-time. 
However, this module serves more than its usual definition and ultimately leads us to obtain geodesics of particles in a spacetime with high curvature, where notions of Newtonian physics fail.
\subsubsection{Schwarzschild Metric \citep{Schwarzschild:1916uq}} \label{subsubsec:sch}
Karl Schwarzschild pioneered the analysis of the relation between the size of black hole and its mass and this work paved the way for the first exact solution of Einstein's Field Equation under the limited case of single spherical non-rotating, non-charged body. 
The metric equation corresponding to a space-time centred around a body in the above described conditions is given by,

@@

%The same equation can be written in a tonsorial form as follows,

@@

We thank all the people that have made EinsteinPy what it is today.  
The generous sponsorship by European Space Agency during Summer of Code in Space really helped us with the betterment of code. We would like to thank the awesome poliastro \citep{juan_luis_cano_rodriguez_2019_3588160} for always motivating us and for being the first sponsor for the project. We would also like to thank our host university, Indian institute of Technology, Mandi who provided us with significant support and have our deepest thanks.
We would specially like to thank Prof.Abhay Ashtekar for his motivational email and  Prof. Timothy A. Gonsalves for his constant motivation and support.
Lastly, we thank all our contributors who contributed selflessly for building this amazing software called EinsteinPy.

@@

\software{astropy \citep{astropy:2013} \citep{astropy:2018},  
          Numpy \citep{numpy}, 
          scipy \citep{2019arXiv190710121V},
          numba \citep{Lam2015NumbaAL},
          matplotlib \citep{matplotlib}
          }

@@

\bibliography{bibliography}{}
\bibliographystyle{aasjournal}
